Evaluating infectious disease forecasts with allocation scoring rules

### 2023-03-31 alloscore_manuscript/allocation.rmd
attempt to sum up central mathematical ideas

>>>>

\textbf{1st attempt by APG to rephrase last paragraph}

The central mathematical ideas in this construction are that 
\begin{itemize}
\item optimization under a \emph{single} constraint requires the rates of change of (a probabilistic forecast's) expected benefit with respect to our decision variables, $x_i$, to be the same for all locations 
\item these rates of change can be identified with probabilities
\item and therefore the Bayes act results from using a \emph{shared} probability level, $1 - \lambda^{\star}/L$, to determine allocations as the corresponding quantiles of the location-specific forecast distributions $F_i$ which satisfy the constraint.
\end{itemize}
(See the supplement for detailed discussion and derivations of these points.)
